### 2012-10-03 3.tex
Writing on chapters 2, 4
Edits to 2 and 4, and writing in 3

\citet{Chomsky1965} argue that speakers internalize not only generalizations governing phonological alternations in their language, but also about the shapes of possible words in their language. It is certainly possible to imagine that speakers would not bother at all. \citet[][320]{Zimmer1969} claims these generalizations ``have no observable consequences in the course of the normal use of the language'' and a similar sentiment is echoed more recently by \citeauthor{PE}:

@@

This is a principled null hypothesis, but one which can be quickly rejected. \citeauthor{Chomsky1965} point to robust contrasts between equally unattested items like *\emph{blick}, which is recognized by speakers a possible word of English, and *\emph{bnick}, which is not.
This preference must be regarded as a learned behavior, since many languages permit  \emph{bn} onsets (e.g., Moroccan Arabic \emph{bni} `building', \emph{bnat} `daughters', \emph{bniqa} `closet'). It is also possible to show speakers access this knowledge not just in wordlikeness judgement tasks but also in naturalistic and quotidien tasks like segmenting spontaneous speech into words, as \citet{McQueen1998} and \citet{Mattys2001b} argue for adult and infant subjects, respectively.

\citeauthor{Chomsky1965} were not the first to take an interest in characterizing the lexicon, which was also a major concern for the scholars of the Copenhagen school. In two sophisticated studies dealing with possible and impossible onsets in Georgian, \citet{Fischer-Jorgensen1952} and \citet{Vogt1954} recognize the inherent difficulty of distinguishing between structural and accidental phonotactic gaps in the lexicon on the basis of statistical criteria alone. What distinguishes the early generativist approach to phonotactics is the mentalistic concern with what generalizations speakers have internalized. By grounding the study of phonotactics in the minds of speakers, it is possible to give a precise definition to the previously vague notions; an accidental phonotactic gap is simply one which speakers do not attend to or internalize. Yet few studies of phonotactics are explicitly concerned with what speakers have internalized, despite the increasing sophistication of the phonological representations used. In a seminal paper, \citet{McCarthy1988} uses a simple statistical technique, a chi-square test, in an attempt to validate a generalization about Arabic root consonant co-occurrence faces originally due to \citet{Greenberg1950}. While this particular generalization was ultimately also evaluated using a wordlikeness task \citep{Frisch2004}, there is now an extensive literature in which phonotactic knowledge is inferred directly from lexical statistics, with no psycholinguistic component of any kind \citep[e.g.,][]{Mester1988,Padgett1992,Padgett1995,Berkley1994b,Berkley1994a,Berkley2000,Buckley1997,MacEachern1999,Kinney2005,Kawahara2006,Martin2007,Martin2011,Pozdniakov2007,Anttila2008,Coetzee2008a,Dmitrieva2008a,Dmitrieva2008b,Graff2011}. The (usually tacit) assumption of most of this work is made explicit by \citet{Brown2010} in his study of consonant cluster co-occurrence restrictions in Gitksan: any statistically significant pattern in the lexicon is one that is internalized by speakers.

@@

\begin{example}[Turkish vowel features]
\begin{tabular}{c | c c c c}
                       & \multicolumn{2}{c}{[$-$\textsc{Back}]} & \multicolumn{2}{c}{[$+$\textsc{Back}]} \\
                       & [$-$\textsc{Round}] & [$+$\textsc{Round}] & [$-$\textsc{Round}] & [$+$\textsc{Round}] \\ \midrule
\buf[$+$\textsc{High}] & \emph{i} & \emph{ü} [y] & \emph{ı} [ɯ] & \emph{u} \\
\buf[$-$\textsc{High}] & \emph{e} & \emph{ö} [ø] & \emph{a} [ɑ] & \emph{o} \\
\end{tabular}
\end{example}

@@

%\citep[after][229]{Clements1982}: \\
\begin{example}[\textsc{Backness Harmony}]
\xymatrix@R=24pt@C=24pt{
\txt{V}                                        & \txt{C$_0$~~~~~} & \txt{V} & \txt{(condition: rightward application)} \\
\txt{[α \textsc{Back}]}\ar@{-}[u]\ar@{--}[urr] \\
}
\end{example}

@@

\begin{example}[The Turkish nominative] \label{turknom}
\begin{tabular}{l l l l l}
   & nom.sg.      & nom.pl. \\
a. & \emph{ip}    & \emph{ipler}    & `rope'        & \citep[][216]{Clements1982} \\
   & \emph{el}    & \emph{eller}    & `hand'    \\
   & \emph{köy}   & \emph{köyler}   & `village' \\
   & \emph{yüz}   & \emph{yüzler}   & `face'    \\
   & \emph{kız}   & \emph{kızlar}   & `girl'    \\
   & \emph{sap}   & \emph{saplar}   & `stalk'   \\
   & \emph{son}   & \emph{sonlar}   & `end'     \\
   & \emph{pul}   & \emph{pullar}   & `stamp'   \\
b. & \emph{neden} & \emph{nedenler} & `reason'       & (TELL) \\ % front
   & \emph{kiler} & \emph{kilerler} & `pantry'       \\ % front
   & \emph{pelür} & \emph{pelürler} & `tissue paper' \\ % back
   & \emph{boğaz} & \emph{boğazlar} & `throat'       \\ % back
   & \emph{sapık} & \emph{sapıklar} & `pervert'      \\ % back
\end{tabular}
\end{example}

@@

\begin{example}[Exceptional Turkish nominatives] \label{turkexcept}
\begin{tabular}{l l l l l}
   & {nom.sg.}    & {nom.pl.} \\
a. & \emph{mezar} & \emph{mezarlar} & `grave' & \citep{TELL} \\
   & \emph{model} & \emph{modeller} & `model' \\
   & \emph{silah} & \emph{silahlar} & `weapon'     \\
   & \emph{memur} & \emph{memurlar} & `bureaucrat' \\
   & \emph{sabun} & \emph{sabunlar} & `soap'       \\
b. & \emph{saat}  & \emph{saatler}  & `hour, clock' \\
   & \emph{harf}  & \emph{harfler}  & `(alphabetic) letter' \\ %& \citep{Goksel2005}
   & \emph{etol}  & \emph{etoller}  & `fur stole' \\
\end{tabular}
\end{example}

@@

\begin{example}[Underspecification in harmonic roots (after \citealp{Clements1982})] \label{spec}
\xymatrix@R=24pt@C=24pt{
\txt{a.} & \txt{harmonic root:~~~~} & \txt{C} & \txt{V} & \txt{C} & \txt{V} & \txt{\ldots} \\
&   &    & \txt{[$-$\textsc{Back}]}\ar@{-}[u]\ar@{--}[urr] \\
\txt{b.} & \txt{disharmonic root:} & \txt{C} & \txt{V} & \txt{C} & \txt{V} & \txt{\ldots} \\
    &    &         & \txt{[$-$\textsc{Back}]}\ar@{-}[u] & & \txt{[$+$\textsc{Back}]}\ar@{-}[u]
}
\end{example}

@@

\begin{example}[Adaptation of initial foreign clusters (\citealp{Clements1982}:247)] 
\begin{tabular}{l l l l l l}
a. & \emph{spiker}  & \alt{} & \emph{sipiker}  & `announcer' \\
   & \emph{fren}    & \alt{} & \emph{firen}    & `break'     \\
b. & \emph{brom}    & \alt{} & \emph{burom}    & `bromide'   \\
   & \emph{prusya}  & \alt{} & \emph{purusya}  & `Prussia'   \\
%b. & grip    & \alt{} & gırip    & `grippe'    \\ % unexpectedly back
%   & kredi   & \alt{} & kıredi   & `credit'    \\
%   & trablus & \alt{} & tırablus & `Tripoli'   \\
%b. & kral    & \alt{} & kıral    & `king'      \\
%   & grup    & \alt{} & gurup    & `group'     \\
\end{tabular}
\end{example}

@@

\begin{example}[Turkish reduplication game (\citealp{Harrison2001}:231)] \label{redupgame}
\begin{tabular}{l l l l}
a. & \emph{kibrit} & \emph{kibrit}-\{\emph{kabrıt}\} & `match'    \\
   & \emph{bütün}  & \emph{bütün}-\{\emph{batın}\}   & `whole'    \\
b. & \emph{mali}   & \emph{mali}-\{\emph{muli}\}     & `Mali'     \\
   & \emph{butik}  & \emph{butik}-\{\emph{batik}\}   & `boutique' \\
\end{tabular}
\end{example}

@@

\begin{example}[\textsc{Roundness Harmony}]
\xymatrix@R=24pt@C=24pt{
\txt{[α \textsc{Round}]}\ar@{-}[d]\ar@{--}[drr] &             & \txt{[$+$\textsc{High}]} \\
\txt{V}                                         & \txt{C$_0$} & \txt{V}\ar@{-}[u] \\
}
\end{example}

@@

\begin{example}[Turkish nominal suffix allomorphy]
\begin{tabular}{l l l l l l l}
   & {nom.sg.}    & {dat.sg.}     & {gen.sg.}  \\
a. & \emph{ip}    & \emph{ipi}    & \emph{ipin}    & `rope' & \citep[][216]{Clements1982} \\
   & \emph{el}    & \emph{eli}    & \emph{elin}    & `hand'    \\
   & \emph{kız}   & \emph{kızı}   & \emph{kızın}   & `girl'    \\
   & \emph{sap}   & \emph{sapı}   & \emph{sapın}   & `stalk'   \\
   & \emph{yüz}   & \emph{yüzü}   & \emph{yüzün}   & `face'    \\
   & \emph{köy}   & \emph{köyü}   & \emph{köyün}   & `village' \\
   & \emph{pul}   & \emph{pulu}   & \emph{pulun}   & `stamp'   \\
   & \emph{son}   & \emph{sonu}   & \emph{sonun}   & `end'     \\
b. & \emph{boğaz} & \emph{boğazı} & \emph{boğazın} & `throat'  & (TELL) \\
   & \emph{pelür} & \emph{pelürü} & \emph{pelürün} & `tissue paper' \\
   & \emph{döviz} & \emph{dövizi} & \emph{dövizin} & `currency' \\
   & \emph{yamuk} & \emph{yamuğu} & \emph{yamuğun} & `trapezoid' \\
   & \emph{ümit}  & \emph{ümiti}  & \emph{ümitin}  & `hope'     \\
\end{tabular}
\end{example}

@@

\begin{example}[\textsc{Labial Attraction}]
%(after \citealt[][286]{Lees1966b}, \citealt[][171]{Inkelas2001}): 
\xymatrix@R=24pt@C=8pt{
\txt{[$-$\textsc{Round}]} &                                         & \txt{[$-$\textsc{High}]} & \txt{[$+$\textsc{Labial}]}    & \txt{[$+$\textsc{High}]}\ar@{-}[dr] &         & \txt{[$+$\textsc{Round}]}\ar@{--}[dl] \\
%                         & \txt{V}\ar@{-}[ul]\ar@{-}[ur]\ar@{-}[d] &                           & \txt{C}\ar@{-}[u] &                                      & \txt{V} & \\
                         & \txt{V}\ar@{-}[ul]\ar@{-}[ur]\ar@{-}[d] &                           & \txt{C$_0$ C C$_0$}\ar@{-}[u] &                                      & \txt{V} & \\
                         & \txt{[$+$\textsc{Back}]}\ar@{-}[urrrr]
}
\end{example}

@@

\begin{example}[Backness harmony wordlikeness forced choices (\citealp{Zimmer1969}:314)]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
\emph{pemez} & 30            & \emph{pemaz} & 2  \\
\emph{tipez} & 24            & \emph{tipaz} & 8  \\ 
\emph{terüz} & 19            & \emph{teruz} & 13 \\ % roundness violator
\emph{teriz} & 28            & \emph{terız} & 3  \\
\emph{tokaz} & 26            & \emph{tokez} & 6  \\ % roundness violator
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Wordlikeness comparisons, roundness harmony]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
\emph{pörüz} & 32            & \emph{pöriz} & 0  \\
\emph{tatız} & 20            & \emph{tatuz} & 12 \\
\emph{tüpüz} & 31            & \emph{tüpiz} & 1  \\
\emph{takız} & 22            & \emph{takuz} & 10 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Wordlikeness comparisons]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{\emph{a}P\emph{u}} & \multicolumn{2}{l}{\emph{a}P\emph{ı}} \\
\midrule
\emph{pamuz} & 17       & \emph{pamız} & 15 \\
\emph{tafuz} & 21       & \emph{tafız} & 11 \\
\emph{tapuz} & 17       & \emph{tapız} & 15 \\
\emph{mavuz} & 16       & \emph{mavız} & 16 \\
\emph{tabuz} & 16       & \emph{tabız} & 16 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Arabic stative verbs]
\begin{tabular}{l l l l}
\hspace{0pt}[kabiːr]  & `big'      & [kabura]  & `become big'       \\
\hspace{0pt}[ħasan]   & `handsome' & [ħasuna]  & `become beautiful' \\
\hspace{0pt}[dʒadiːb] & `barren'   & [dʒaduba] & `become dry'       \\
\end{tabular}
%b. & saʁiir & }`become small'     & (cf. \emph{saʁiːr} `small') \\
\end{example}

@@

\begin{example}[\textsc{Labial harmony} and etymology in TELL \citealp{Inkelas2001}:187]
\begin{tabular}{l r r r}
        & \emph{a}P\emph{u} & \emph{a}P\emph{ı} & $p$-value \\
Native  & 12                & 11                & \multirow{2}{*}{0.042} \\
Foreign & 84                & 28                \\
\end{tabular}
\end{example}

>>>>

While \citet{Chomsky1965} argue that speakers internalize facts about the shapes of possible words in their language, it is certainly possible to imagine that speakers would not bother at all. \citet[][320]{Zimmer1969} claims these generalizations ``have no observable consequences in the course of the normal use of the language'' and a similar sentiment is echoed more recently by \citeauthor{PE}:

@@

This represents a principled null hypothesis, but it can be quickly dismissed. 
This might represent

This would be a principled null hypothesis, but it can be quickly rejected in light of the indisputable contrast between non-words like \emph{blick} and \emph{bnick} noted by \citeauthor{Chomsky1965}. It is also possible to show speakers access this knowledge not just in metalinguist tasks like wordlikeness judgements, but also in such naturalistic and quotidien tasks as segmenting spontaneous speech into words \citep{Mattys2001b,McQueen1998}.

\citeauthor{Chomsky1965} were not the first to take an interest in characterizing the lexicon, which was also a major concern for the scholars of the Copenhagen school. In two sophisticated studies dealing with possible and impossible onsets in Georgian, \citet{Fischer-Jorgensen1952} and \citet{Vogt1954} recognize the inherent difficulty of distinguishing between structural and accidental phonotactic gaps in the lexicon on the basis of statistical criteria alone. What distinguishes the early generativist approach to phonotactics is the mentalistic concern with what generalizations speakers have internalized. By grounding the study of phonotactics in the minds of speakers, it is possible to give a precise definition to the previously vague notions; an accidental phonotactic gap is simply one which speakers do not attend to or internalize. Yet few studies of phonotactics are explicitly concerned with what speakers have internalized, despite the increasing sophistication of the phonological representations used. In a seminal paper, \citet{McCarthy1988} uses a simple statistical technique, a chi-square test, in an attempt to validate a generalization about Arabic root consonant co-occurrence faces originally due to \citet{Greenberg1950}. While this particular generalization was ultimately also evaluated using a wordlikeness task \citep{Frisch2004}, there is now an extensive literature in which phonotactic knowledge is inferred directly from lexical statistics, with no psycholinguistic component of any kind 
\citep[e.g.,][]{Anttila2008,
Berkley1994b,Berkley1994a,Berkley2000,
Brown2010,
Buckley1997,
Coetzee2008a,
Dmitrieva2008a,Dmitrieva2008b,
Elmedlaoui1995,
Graff2011,
Padgett1992,Padgett1995,
MacEachern1999,
Kinney2005,
Kawahara2006,
Martin2007,Martin2011,
Mester1988,
Miller-Ockhuizen2003,
Pozdniakov2007,
Yip1989}.
%find amanda miller-ockhuizen on ju|'hoansi
The (usually tacit) assumption of most of this work is made explicit by \citet{Brown2010} in a study of consonant cluster co-occurrence restrictions in Gitksan: he claims that \emph{any} statistically significant pattern in the lexicon is one that is internalized by speakers.

@@

\begin{example}[Turkish vowel features]
\begin{tabular}{c c c c c}
                       & \multicolumn{2}{c}{[$-$\textsc{Back}]} & \multicolumn{2}{c}{[$+$\textsc{Back}]} \\
                       & [$-$\textsc{Round}] & [$+$\textsc{Round}] & [$-$\textsc{Round}] & [$+$\textsc{Round}] \\ %\midrule 
\buf[$+$\textsc{High}] & {i} & {ü} [y] & {ı} [ɯ] & {u} \\
\buf[$-$\textsc{High}] & {e} & {ö} [ø] & {a} [ɑ] & {o} \\
\end{tabular}
\end{example}

@@

\begin{example}[\textsc{Backness Harmony}]
$\begin{bmatrix} +\textsc{Vocalic} \end{bmatrix}~\goesto~\begin{bmatrix} =\textsc{Back} \end{bmatrix}~\big /~\begin{bmatrix} =\textsc{Back} \end{bmatrix}~\textrm{C}_0~\gap{}$
\end{example}

%\citep[after][229]{Clements1982}: \\
%\xymatrix@R=24pt@C=24pt{
%\txt{V}                                        & \txt{C$_0$~~~~~} & \txt{V} & \txt{(condition: rightward application)} \\
%\txt{[α \textsc{Back}]}\ar@{-}[u]\ar@{--}[urr] \\
%}

@@

\begin{example}[The Turkish nominative] \label{turknom}
\begin{tabular}{l l l l@{ }l}
   & \emph{nom.sg.} & \emph{nom.pl.} \\
a. & {ip}           & {ipler}    & `rope'        & \citep[][216]{Clements1982} \\
   & {el}           & {eller}    & `hand'    \\
   & {köy}          & {köyler}   & `village' \\
   & {yüz}          & {yüzler}   & `face'    \\
   & {kız}          & {kızlar}   & `girl'    \\
   & {sap}          & {saplar}   & `stalk'   \\
   & {son}          & {sonlar}   & `end'     \\
   & {pul}          & {pullar}   & `stamp'   \\
b. & {neden}        & {nedenler} & `reason'       & (TELL) \\ % front
   & {kiler}        & {kilerler} & `pantry'       \\ % front
   & {pelür}        & {pelürler} & `tissue paper' \\ % back
   & {boğaz}        & {boğazlar} & `throat'       \\ % back
   & {sapık}        & {sapıklar} & `pervert'      \\ % back
\end{tabular}
\end{example}

@@

\begin{example}[Exceptional Turkish nominatives] \label{turkexcept}
\begin{tabular}{l l l l@{ }l}
   & \emph{nom.sg.} & \emph{nom.pl.} \\
a. & {mezar}        & {mezarlar} & `grave' & \citep{TELL} \\
   & {model}        & {modeller} & `model' \\
   & {silah}        & {silahlar} & `weapon'     \\
   & {memur}        & {memurlar} & `bureaucrat' \\
   & {sabun}        & {sabunlar} & `soap'       \\
b. & {saat}         & {saatler}  & `hour, clock' \\
   & {harf}         & {harfler}  & `(alphabetic) letter' \\ %& \citep{Goksel2005}
   & {etol}         & {etoller}  & `fur stole' \\
\end{tabular}
\end{example}

@@

\begin{example}[Autosegmental underspecification in harmonic roots (after \citealp{Clements1982})] \label{spec}
\xymatrix@R=24pt@C=24pt{
\txt{a.} & \txt{harmonic root:~~~~} & \txt{C} & \txt{V} & \txt{C} & \txt{V} & \txt{\ldots} \\
&   &    & \txt{[$-$\textsc{Back}]}\ar@{-}[u]\ar@{--}[urr] \\
\txt{b.} & \txt{disharmonic root:} & \txt{C} & \txt{V} & \txt{C} & \txt{V} & \txt{\ldots} \\
    &    &         & \txt{[$-$\textsc{Back}]}\ar@{-}[u] & & \txt{[$+$\textsc{Back}]}\ar@{-}[u]
}
\end{example}

@@

\begin{example}[Adaptation of initial foreign clusters (\citealp{Clements1982}:247)] 
\begin{tabular}{l l l l l l}
a. & {spiker}  & \alt{} & {sipiker}  & `announcer' \\
   & {fren}    & \alt{} & {firen}    & `break'     \\
b. & {brom}    & \alt{} & {burom}    & `bromide'   \\
   & {prusya}  & \alt{} & {purusya}  & `Prussia'   \\
%b. & grip    & \alt{} & gırip    & `grippe'    \\ % unexpectedly back
%   & kredi   & \alt{} & kıredi   & `credit'    \\
%   & trablus & \alt{} & tırablus & `Tripoli'   \\
%b. & kral    & \alt{} & kıral    & `king'      \\
%   & grup    & \alt{} & gurup    & `group'     \\
\end{tabular}
\end{example}

@@

\begin{example}[Turkish reduplication game (\citealp{Harrison2001}:231)] \label{redupgame}
\begin{tabular}{l l l l}
a. & {kibrit} & {kibrit}-\{{kabrıt}\} & `match'    \\
   & {bütün}  & {bütün}-\{{batın}\}   & `whole'    \\
b. & {mali}   & {mali}-\{{muli}\}     & `Mali'     \\
   & {butik}  & {butik}-\{{batik}\}   & `boutique' \\
\end{tabular}
\end{example}

@@

%\begin{example}[\textsc{Roundness Harmony}]
%\xymatrix@R=24pt@C=24pt{
%\txt{[α \textsc{Round}]}\ar@{-}[d]\ar@{--}[drr] &             & \txt{[$+$\textsc{High}]} \\
%\txt{V}                                         & \txt{C$_0$} & \txt{V}\ar@{-}[u] \\
%}
%\end{example}

@@

\begin{example}[Turkish nominal suffix allomorphy]
\begin{tabular}{l l l l l l@{ }l}
   & \emph{nom.sg.} & \emph{dat.sg.} & \emph{gen.sg.}  \\
a. & {ip}           & {ipi}          & {ipin}         & `rope' & \citep[][216]{Clements1982} \\
   & {el}           & {eli}          & {elin}         & `hand'    \\
   & {kız}          & {kızı}         & {kızın}        & `girl'    \\
   & {sap}          & {sapı}         & {sapın}        & `stalk'   \\
   & {yüz}          & {yüzü}         & {yüzün}        & `face'    \\
   & {köy}          & {köyü}         & {köyün}        & `village' \\
   & {pul}          & {pulu}         & {pulun}        & `stamp'   \\
   & {son}          & {sonu}         & {sonun}        & `end'     \\
b. & {boğaz}        & {boğazı}       & {boğazın}      & `throat'  & (TELL) \\
   & {pelür}        & {pelürü}       & {pelürün}      & `tissue paper' \\
   & {döviz}        & {dövizi}       & {dövizin}      & `currency' \\
   & {yamuk}        & {yamuğu}       & {yamuğun}      & `trapezoid' \\
   & {ümit}         & {ümiti}        & {ümitin}       & `hope'     \\
\end{tabular}
\end{example}

@@

%\begin{example}[\textsc{Labial Attraction}]
%%(after \citealt[][286]{Lees1966b}, \citealt[][171]{Inkelas2001}): 
%\xymatrix@R=24pt@C=8pt{
%\txt{[$-$\textsc{Round}]} &                                         & \txt{[$-$\textsc{High}]} & \txt{[$+$\textsc{Labial}]}    & \txt{[$+$\textsc{High}]}\ar@{-}[dr] &         & \txt{[$+$\textsc{Round}]}\ar@{--}[dl] \\
%%                         & \txt{V}\ar@{-}[ul]\ar@{-}[ur]\ar@{-}[d] &                           & \txt{C}\ar@{-}[u] &                                      & \txt{V} & \\
%                         & \txt{V}\ar@{-}[ul]\ar@{-}[ur]\ar@{-}[d] &                           & \txt{C$_0$ C C$_0$}\ar@{-}[u] &                                      & \txt{V} & \\
%                         & \txt{[$+$\textsc{Back}]}\ar@{-}[urrrr]
%}
%\end{example}

@@

\begin{example}[Backness harmony wordlikeness forced choices (\citealp{Zimmer1969}:314)]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
{pemez} & 30            & {pemaz} & 2  \\
{tipez} & 24            & {tipaz} & 8  \\ 
{terüz} & 19            & {teruz} & 13 \\ % roundness violator
{teriz} & 28            & {terız} & 3  \\
{tokaz} & 26            & {tokez} & 6  \\ % roundness violator
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Wordlikeness comparisons, roundness harmony]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
{pörüz} & 32            & {pöriz} & 0  \\
{tatız} & 20            & {tatuz} & 12 \\
{tüpüz} & 31            & {tüpiz} & 1  \\
{takız} & 22            & {takuz} & 10 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Wordlikeness comparisons]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{{a}P{u}} & \multicolumn{2}{l}{{a}P{ı}} \\
\midrule
{pamuz} & 17       & {pamız} & 15 \\
{tafuz} & 21       & {tafız} & 11 \\
{tapuz} & 17       & {tapız} & 15 \\
{mavuz} & 16       & {mavız} & 16 \\
{tabuz} & 16       & {tabız} & 16 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Arabic stative verbs]
\begin{tabular}{l l l l}
\buf{}[kabiːr]  & `big'      & [kabura]  & `become big'       \\
\buf{}[ħasan]   & `handsome' & [ħasuna]  & `become beautiful' \\
\buf{}[dʒadiːb] & `barren'   & [dʒaduba] & `become dry'       \\
\end{tabular}
%b. & saʁiir & }`become small'     & (cf. \emph{saʁiːr} `small') \\
\end{example}

@@

\begin{example}[\textsc{Labial harmony} and etymology in TELL \citealp{Inkelas2001}:187]
\begin{tabular}{l r r r}
        & {a}P{u} & {a}P{ı} & $p$-value \\
native  & 12                & 11                & \multirow{2}{*}{0.042} \\
foreign & 84                & 28                \\
\end{tabular}
\end{example}
